%%%%
% Chehab Hanys Resume
%%%%
% Author: Chehab Hany
% License: CC-BY-4
% - https://creativecommons.org/licenses/by/4.0/legalcode.txt
%%%%

\documentclass[letterpaper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
%% NOTE: Everything between here and END_FILE can
%% be relocated to "mteck.sty" and then included with:
%\usepackage{mteck}

% Dependencies
% NOTE: Some packages (lastpage, hyperref) require second build!
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}

% Sans-Serif
%\usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
%\usepackage[sfdefault]{noto-sans}
%\usepackage[default]{sourcesanspro}

% Serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% Colors
% Use with \color{Name}
% Can wrap entire heading with {\color{accent} [...] }
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

%-----------------%
% Custom Commands %
%-----------------%

% Centered title along with subtitle between HR
% Usage: \documentTitle{Name}{Details}
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\scshape\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    %{\footnotesize\color{accentTitle} #2}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

% Create a footer with correct padding
% Usage: \documentFooter{\thepage of X}
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

% Simple wrapper to set up page numbering
% Usage: \numberedPages
% WARNING: Must run pdflatex twice!
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

% Section heading with horizontal rule
% Usage: \section{Title}
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \scshape\raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

% Section heading with separator and content on same line
% Usage: \tinysection{Title}
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\scshape\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

% Indented line with arguments left/right aligned in document
% Usage: \heading{Left}{Right}
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

% Adds \textbf to \heading
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

% Adds \textit to \heading
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

% Template for itemized lists
% Usage: \begin{resume_list} [items] \end{resume_list}
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
  %\vspace{-2pt}
}

% Formats an item to use as an itemized title
% Usage: \itemTitle{Title}
\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}

% Bullets used in itemized lists
\renewcommand\labelitemi{--}

%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%


%===================%
% Chehab Hany's Resume %
%===================%

%\numberedPages % NOTE: lastpage requires a second build
%\documentFooter{\thepage of 2} % Does similar without using lastpage
\begin{document}

  %---------%
  % Heading %
  %---------%

  \documentTitle{Chehab Hany}{
    % Web Version
    %\raisebox{-0.05\height} \faPhone\ [redacted - web copy] ~
    %\raisebox{-0.15\height} \faEnvelope\ [redacted - web copy] ~
    %%
    \href{tel:01522-41777-57}{
      \raisebox{-0.05\height} \faPhone\ +49-1522-41-77757} ~
    \href{mailto:chehabhany90@gmail.com}{
      \raisebox{-0.15\height} \faEnvelope\ chehabhany90@gmail.com} ~
    \href{https://linkedin.com/in/chehabhany/}{
      \raisebox{-0.15\height} \faLinkedin\ linkedin.com/in/chehabhany} ~
    \href{https://github.com/chippo90}{
      \raisebox{-0.15\height} \faGithub\ github.com/chippo90}
  }

  %---------%
  % Objective %
  %---------%

  \tinysection{Objective}
  To gain valuable experience in a qualified company, where I can invest and develop my skills, experience and potential I rewarded and challenging a new position with career development based on performance.

  %------------%
  % Experience %
  %------------%

  \section{Professional Career}

  \headingBf{Asian Paints Berger - Qatar}{Jun 2021 -- Apr 2024}
  \headingIt{Senior Executive - Projects}{}
  \begin{resume_list}
    \item Created new customers by planning, frequent visits to potential customers and preparing quotations to increase market share.
    \item Worked with consultants, specifiers and contractors to get our materials specified and approved in each project.
    \item Followed up with customers on payments, balance reconciliation and cheque collection.
    \item Coordinated internally with other departments (such as Customer Service, Logistics, etc.) to ensure on-time delivery.
    \item Prepared project pipeline, monthly sales reports and updated sales activities.
  \end{resume_list}

  \headingBf{Fischer - Qatar}{Apr 2017 -- May 2021}
  \headingIt{Key Project Engineer - Sales}{}
  \begin{resume_list}
    \item Played an integral role in new business pitches and hold responsibility for the effective on-boarding of new projects.
    \item Focused on growing and developing existing projects, together with generating new business.
    \item Acquired a thorough understanding of key project needs and requirements.
    \item Expanded the relationships with existing customers by continuously proposing solutions that meet their objectives.
    \item Acted as the key interface between the customer and all relevant divisions.
    \item Ensured the correct products and services are delivered to customers in a timely manner.
    \item Resolved any issues and problems faced by customers and deal with complaints to maintain trust.
  \end{resume_list}

 \headingBf{Unitech - Qatar}{Jan 2016 -- Mar 2017}
  \headingIt{Sales Engineer}{}
  \begin{resume_list}
    \item Utilized sales skills to probe, build and cross-sell directly on site to customers through our product, market and service knowledge.
    \item Ensured adherence to Unitech's quality philosophy while supporting the Company strategy and culture to exceed customers' expectations.
    \item Performed marketing launches and promotions to customers and provided business solutions fully adapted to customers’ needs.
    \item Handled customers financial issues related to Unitech, also negotiated and signed agreements “credit agreements and price agreements”
  \end{resume_list}
  
  %-----------%
  % Education %
  %-----------%

  \section{Education}

  \headingBf{Gisma University of Applied Sciences - Germany}{} % Note: Adding year(s) exposes an implied age
  \headingIt{Bachelor of Software Engineering - 2027}{}
  \vspace{5pt}
  \headingBf{Alexandria Higher Institute of Engineering and Technology - Egypt}{} % Note: Adding year(s) exposes an implied age
  \headingIt{Bachelor of Electronics and Communications Engineering - 2014}{}
  \vspace{5pt}
  \headingBf{Training and Courses}{}
  \begin{resume_list}
    \item Professional Selling Skills \hspace{2pt}- from Human Training Consultants.
    \item Basic Product Training - from Fischer Regional Training Center
  \end{resume_list}

  %----------------------------%
  % Language Skills %
  %----------------------------%

  \section{Language Skills}

  \headingBf{Arabic - Native Speaker}{}
    \vspace{5pt}
  \headingBf{English - Advanced C1}{}
    \vspace{5pt}
  \headingBf{French - Intermediate B1}{}
    \vspace{5pt}
  \headingBf{German - Beginner A1}{}

\end{document}