
\documentclass[12pt, letterpaper]{template}
\title{Chehab Hany Mohamed Elsayed Elsayed Elmenoufi}
\author{Student Number\\GH 1034223}
\supervisor{Dr. Mehran Monavari}


\begin{document}


\chapter{Introduction}\label{ch:in}

\paragraph {\Large In the digital age, the online presence is essential for individuals and organizations as well. This assessment involves the development of a responsive and interactive HTML web page designed to serve as my portfolio for showcasing information, skills, and professional experience. The web page is hosted on GitHub repository, ensuring ease of access and navigation.}

\paragraph{\Large The primary objective of this project is to create a clear, fancy, and user-friendly web page that effectively communicates the intended content of its viewer. The web page incorporates HTML for structure, CSS for styling, and JavaScript for interactive elements.}

\paragraph{\Large This report will detail the various aspects of the project, including its features, and usage instructions and the underlying design principles. Also, it will provide an overview of the technologies used and the ideas behind key design decisions. By the end of this report, you will have a thorough understanding of the project's scope and implementation.}
\chapter{Project Design}

\paragraph{\Large The first step I have done is creating an account on GitHub with a username of chippo90. Then I have created my own repository carrying the same user name, I have made it public in order to include all the projects I will work on for this module. The link for my repository is as below:}
\begin{center}
    \Large\url{ https://github.com/Chippo90/chippo90.github.io.git}
\end{center}

\paragraph{\Large Since the repository is ready to receive my file, the second step is to create a file index.html, CSS folder, JS folder, and assets folder for my images. This should include all my HTML work for my portfolio web page}

\begin{itemize}
\item \Large \textbf{HTML}
\end{itemize}

\paragraph{\Large I have chosen a template from an open source on the web, I have managed to implement my structure and details inside it, I changed icons, fonts and photo, and I adjusted my details to suit my profile. The reference link for the template is as below:-}
\begin{center}
    \Large\url{https://startbootstrap.com/previews/resume}
\end{center}
\paragraph{\Large I started by setting my document type to HTML, the language to be English, and assigning the title of my web page to be "Portfolio Web page - Chehab Hany" and included an icon next to it which is my profile photo and it's stored in my assets folder. Then for styling, I have brought some icons and fonts from the below websites:}
\begin{center}
    \Large\url{www.fontawesome.com}
\end{center}

\begin{center}
    \Large\url{https://fonts.google.com}
\end{center}
\paragraph{\Large After importing these external styling to my CSS folder, I began to work on my fixed part of the page where I have assigned the scroll navigation through JavaScript. I included my name and assigned a circled photo styling for myself and uploaded it on my assets folder.}

\paragraph{\Large Moving forward, I put my titles of my section on the fixed part of my page so whenever you press on any title of them, it will take directly to the desired section. For my page content, I have included my name, address as well as my email address and last was a brief summary about my objective.}

\paragraph{\Large Next, I imported four icons for Linked in, GitHub, Facebook, and Instagram and linked them to my profile pages. Moving to my next section in my content page, Experience, Where I included the three companies I have worked for, I included the dates and the description of the work done with them. I have used heading for my job title, subheading for the company name, and paragraph for the job description.}

\paragraph{\Large Similar to the previous section, I have made another one for my education where I put both my current and previous bachelor degrees accordingly along with details of programs and graduation years. I have used heading for the university name and subheading for the type of degree. Up next, another section for my languages skills, where I included each language along with its correspondent level of knowledge while I have imported a globe icon to start at the beginning of each language skill.}

\paragraph{\Large Finally, for my last two section of my portfolio, a section for my interests where I wrote a paragraph about my hobbies and interests in my free time and last section was for my recognitions and training certifications in which I included all the achievements I have acquired during my career while each recognition starts with an imported icon of a trophy.}

\paragraph{\Large The link for my portfolio web page is as below:-}
\begin{center}
    \Large\url{https://chippo90.github.io}
\end{center}
\begin{itemize}
\item \Large \textbf{\LaTeX}
\end{itemize}

\paragraph{\Large I had two tasks to do on \LaTeX, the first one is to make a resume through it, which I have done from a template on www.overleaf.com and the second task is to make this current project report on it as well, both .pdf and .tex files are available on my GitHub repository for your reference}


\chapter{Conclusion}
\paragraph{\Large In conclusion, the HTML project undertaken has successfully achieved its objectives of creating a dynamic and user-friendly web interface. Throughout this project, a variety of HTML5 elements were utilized to structure the content, ensuring that the layout is pleasing and functional.}

\paragraph{\Large This project has provided me valuable insights into the practical application of HTML in web development. The skills and knowledge gained through this process are great for further exploration and development in web technology.}

\paragraph{\Large As much as I have learned from my lectures among this quarter, I still need to work on my future enhancements to learn more and more about HTML, CSS, and JavaScript. Today, I had the help from many books and templates that showed me the way to design my page. Next time, I plan to include more complex and rich content on my web page, have more details on my page, a video introduction of myself, attaching my certificates and to implement a "Contact Me" section.}
\cite{BeginningHTMLCSS}\cite{HTML&CSS}\cite{JavaScript}
\appendix

\end{document}
